### 2017-09-30 TF-vldb2018/subsec-auxstr.tex

\vspace{0.5ex}
(I) Data structures in the first class are as follows.

@@

\vspace{0.4ex}
\etitle{(4) Fragment-ball-match index (\fb)} links \fs and \bs together, to form the {\em fragment-ball-match index}. Then \fb is linked to $\tilde{M}(P,G)$. \revise{The details are shown below.}

@@

\begin{example}
\label{exa-matchindex}
Consider $P_1$ and $G_1$ (both without dashed edges) in Fig.~\ref{exm-motivation}, $r=2$, $k=2$, $h=2$,
auxiliary structures $\tilde{M}(P,G)$ and \fb\,that are shown in Fig.~\ref{fig-auxiliary-structures}(a).
$P_1$ is divided into fragments $P_{f1}$ and $P_{f2}$ by algorithm \kw{PFrag},
so there are $2^2=4$ type codes in \fs.
For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
Besides, there exist balls $\ball{[\kw{PM_2},2]}$, $\ball{[\kw{BA_3},2]}$ and $\ball{[\kw{PM_4},2]}$
linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively.
We only consider these 4 balls in the sequel.
\end{example}

@@

\vspace{0.5ex}
(II) Data structures in the second class are as follows.

@@

%Algorithm \inc updates and uses \bfc in step (1) for identifying \affballsx for pattern updates.
\vspace{0.5ex}
\etitle{(2) Update planner (\upl)} consists of $h+1$ stacks $T({P}_{f1})$, $\ldots$, $T({P}_{fh})$, $T(C)$.
Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
Initially, all of them are empty.
They are dynamically updated for each unit update in each set of coming pattern updates.

Better still, it holds a nice property as follows.
\begin{theorem}
\label{thm-framework-inc}
With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
\end{theorem}

We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.

>>>>

\stab(I) Data structures in the first class are as follows.

@@

\vspace{0.4ex}
\etitle{(4) Fragment-ball-match index (\fb)} links \fs and \bs together, to form the {\em fragment-ball-match index}. Then \fb is linked to $\tilde{M}(P,G)$. The details are shown below.

@@

\begin{example}
\label{exa-matchindex}
Consider $P_1$ and $G_1$ (both without dashed edges) in Fig.~\ref{exm-motivation}, $r=2$, $k=2$, $h=2$,
auxiliary structures $\tilde{M}(P,G)$ and \fb\,that are shown in Fig.~\ref{fig-auxiliary-structures}(a).

\ni (1) Pattern $P_1$ is divided into fragments $P_{f1}$ and $P_{f2}$ by algorithm \kw{PFrag},
so there are $2^2=4$ type codes in \fs.

\ni (2) For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
Besides, there exist balls $\ball{[\kw{PM_2},2]}$, $\ball{[\kw{BA_3},2]}$ and $\ball{[\kw{PM_4},2]}$
linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively. 
%
For simplicity, we consider these 4 balls only in the sequel.
\end{example}

@@

These structures enforce a nice property as follows.

\begin{theorem}
\label{thm-framework-inc}
With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
\end{theorem}

We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity.

\stab(II) Data structures in the second class are as follows.

@@

%Algorithm \inc updates and uses \bfc in step (1) for identifying \affballsx for pattern updates.
\vspace{0.5ex}
\etitle{(2) Update planner (\upl)} consists of $h+1$ stacks $T({P}_{f1})$, $\ldots$, $T({P}_{fh})$, $T(C)$.
Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
Initially, all of them are empty, and are dynamically updated for each unit update in each coming set of  pattern updates.
